[dcpo_demsupport]

### 2020-08-02 paper/dcpo_demsupport.Rmd
finishing the visualization of dcpo outcomes, task of #4

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

```{r dcpo-uncertainty}
# Preload function ----
vcovBK_se <- function(x) {
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

# load(here::here("data", "dcpo_input_update.rda"))
load(here::here("data", "dcpo_theta.rda"))

@@

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset
  )
})

@@

summary(mitools::MIcombine(results = result_betas_dcpo_1k, 
                           variance = result_vars_dcpo_1k))

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

```{r dcpo-uncertainty, cache=TRUE}
# Preload function ----
vcovBK_se <- function(x) {
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))

@@

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset
  )
})

@@

df_result_dcpo <- summary(mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)) %>% rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)"))

```{r dcpoVisualization, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

(dwplot(df_result_dcpo, by_2sd = FALSE)) %>% 
  relabel_predictors(c(`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")
